---
title: "**Modul 1: Introduction to R for Data Analytics**"
author: "Muhammad Apriandito - Digital Business Experience"
output:
  html_document:
    theme: paper
    highlight: tango
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "png", 
                      dev.args = list(type = "cairo-png"), 
                      fig.height = 5, 
                      fig.width = 9, 
                      tidy='styler', tidy.opts=list(strict=FALSE), 
                      fig.align = "center")
options(scipen=10000)
```

------------------------------------------------------------------------

### **Reading Material**

Please read the following materials before class:

1.  An Introduction to R: <https://intro2r.com/>

2.  R for Data Science: <https://r4ds.had.co.nz/>

------------------------------------------------------------------------

### **Pretest**

Please anwer this following question and submit it in google classroom

1.  How many data types and structures are there in the R programming language?

2.  State the type of control flow?

3.  What do the R Packages mean?

------------------------------------------------------------------------

### **Introduction to R Programming**

R is a popular programming language for statistics and data analytics. In this module we will learn the basics of R programming for data analytics.

#### **Mathematical Operation**

Like other programming languages in general, R can perform mathematical operations such as: addition, subtraction, multiplication, and etc.

```{r eval=FALSE, include= TRUE}
# Addition
5 + 5
```

```{r eval=FALSE, include= TRUE}
# Subtraction
5 - 5
```

```{r eval=FALSE, include= TRUE}
# Multiplication
3 * 5
```

```{r eval=FALSE, include= TRUE}
# Division
5 / 2
```

```{r eval=FALSE, include= TRUE}
# Power
2 ^ 5
```

```{r eval=FALSE, include= TRUE}
# Modulo
28 %% 6
```

#### **Storing value in Variable**

R allows us to store values as variables. To do this, we can use the command `<-` or `=`

```{r}
# Example of store value in variable with "<-"
example_variable <- 4
```

The value stored in a variable is not immediately displayed. We have to use the command `print(varible_name)` to display it.

```{r}
# View the value in a variable with print()
print(example_variable)
```

The following is an example of storing values in a varible using \``=`

```{r}
# Example of store value in variable with "="
example_variable_2 <- 2

# Print Variable
print(example_variable_2)
```

Both commands are working fine. However, in the R community it is more common to use `<-`

#### **Data Type**

R has 5 main data types namely:

##### **Numeric**

```{r}
# Examples of numeric data type
n <- 1.2
```

To see the data type we can use `class(variable_name)` function

```{r}
# View data types of n
class(n)
```

To see the value of the data we can use `print(variable_name)` function, as we have learned before

```{r}
# View data values
print(n)
```

##### **Integer**

```{r}
# Examples of integer data type
i <- 2L
```

##### **Character**

```{r}
# Examples of character data type
c <- "MBA ITB"
```

##### **Logical**

```{r}
# Examples of logical data type
l <- TRUE
```

##### **Complex**

```{r}
# Examples of complex data type
com <- 3 + 2i
```

#### **Data Structure**

R has 5 main data sctructure namely:

##### **Vector**

```{r}
# Example of Vector
v <- c("banana", "apple", "tomato")
```

##### **List**

```{r}
# Example of Vector
li <- list(1, "a", TRUE, 1 + 4i)
```

##### **Matrix**

```{r}
# Example of Matrix
m <- matrix(c(1:3))
```

##### **Factor**

```{r}
# Example of Factor
f <- factor(c(
  "Male",
  "Female",
  "Female",
  "Male",
  "Male",
  "Female"
))
```

##### **Dataframe**

```{r}
df_student <- data.frame(
  name = c("Dito", "Dian", "Rosidi"),
  age = c(22, 23, 27),
  sex = c("Male", "Female", "Male")
)
```

#### **Function**

A function is a set of command lines or code arranged together to perform a specific task. In R, we can use built-in functions or create new ones.

##### **Built-in / Base Functions**

```{r}
# Creating Age Vectors
age <- c(22, 23, 21, 8, 10, 14, 15)
```

```{r}
# Calculates the average age
mean(age)
```

##### **Custom Function**

```{r}
# Create a function to calculate Return of Investment
roi <- function(profit, cost_of_investment) {
  return((profit / cost_of_investment) * 0.1)
}
```

```{r}
# Using the ROI function that has been created
roi(profit = 175, cost_of_investment =  75)
```

#### **Package**

R Package is a collection of functions / functions or data in R. There are many packages created / developed by other users. The following are examples of packages that are commonly used. To be able to use the existing functions in a package, we must install and load the package first.

##### **Readxl**

The readxl package is useful for importing data in .xlsx or .xls format into the R environment.

```{r eval=FALSE, include= TRUE}
# Install package
install.packages("readxl")
```

```{r}
# Load package
library(readxl)
```

```{r}
# Import .xlsx data
df_xlsx <- read_xlsx("data/Sales.xlsx")
```

```{r}
# View Data
head(df_xlsx)
```

##### **Readr**

The readr package is useful for importing data in .csv format or other text formats into the R environment.

```{r eval=FALSE, include= TRUE}
# Install package
install.packages("readr")
```

```{r}
# Load package
library(readr)
```

```{r message=FALSE, warning=FALSE}
# Import .csv data
df_csv <- read_csv("data/Sales.csv")
```

```{r}
# View Data
head(df_csv)
```

------------------------------------------------------------------------

### **Post Test**

1.  Create a dataframe containing information from 10 of your classmates (Name, Age, Gender, Hobbies)

2.  Create a function to calculate the Return on Equity

3.  Find out the 5 R packages and explain their functions/purpose
