---
title: "**Modul 1: Introduction to R for Data Analytics**"
author: "Manahan Siallagan - Muhammad Apriandito"
output:
  html_document:
    theme: paper
    highlight: tango
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  dev = "png",
  dev.args = list(type = "cairo-png"),
  fig.height = 5,
  fig.width = 9,
  tidy = "styler", tidy.opts = list(strict = FALSE),
  fig.align = "center"
)
options(scipen = 10000)
set.seed(1234)
```

------------------------------------------------------------------------

### **Reading Material**

Please read the following material before class starts.

1.  [An Introduction to R](https://intro2r.com/){.uri}

2.  [R for Data Science](https://r4ds.had.co.nz/){.uri}

------------------------------------------------------------------------

### **Pretest**

Based on the reading material above, please answer the following questions and collect the answers via Google Classroom.

1.  How many data types and structures are there in the R programming language?

2.  State the type of control flow?

3.  What do the R Packages mean?

------------------------------------------------------------------------

### **Introduction to R Programming**

R is a popular programming language for statistics and data analytics. In this module we will learn the basics of R programming for data analytics.

#### **Mathematical Operation**

Like other programming languages in general, R can perform mathematical operations such as: addition, subtraction, multiplication, and etc.

```{r eval=FALSE, include= TRUE}
# Addition
5 + 5
```

```{r eval=FALSE, include= TRUE}
# Subtraction
5 - 5
```

```{r eval=FALSE, include= TRUE}
# Multiplication
3 * 5
```

```{r eval=FALSE, include= TRUE}
# Division
5 / 2
```

```{r eval=FALSE, include= TRUE}
# Power
2 ^ 5
```

```{r eval=FALSE, include= TRUE}
# Modulo
28 %% 6
```

#### **Storing value in Variable**

R allows us to store values as variables. To do this, we can use the command `<-` or `=`

```{r}
# Example of store value in variable with "<-"
example_variable <- 4
```

The value stored in a variable is not immediately displayed. We have to use the command `print(varible_name)` to display it.

```{r}
# View the value in a variable with print()
print(example_variable)
```

The following is an example of storing values in a varible using \``=`

```{r}
# Example of store value in variable with "="
example_variable_2 <- 2

# Print Variable
print(example_variable_2)
```

Both commands are working fine. However, in the R community it is more common to use `<-`

#### **Data Type**

R has 5 main data types namely:

##### **Numeric**

```{r}
# Examples of numeric data type
n <- 1.2
```

To see the data type we can use `class(variable_name)` function

```{r}
# View data types of n
class(n)
```

To see the value of the data we can use `print(variable_name)` function, as we have learned before

```{r}
# View data values
print(n)
```

##### **Integer**

```{r}
# Examples of integer data type
i <- 2L
```

##### **Character**

```{r}
# Examples of character data type
c <- "MBA ITB"
```

##### **Logical**

```{r}
# Examples of logical data type
l <- TRUE
```

##### **Complex**

```{r}
# Examples of complex data type
com <- 3 + 2i
```

#### **Data Structure**

R has 5 main data sctructure namely:

##### **Vector**

```{r}
# Example of Vector
v <- c("banana", "apple", "tomato")
```

##### **List**

```{r}
# Example of Vector
li <- list(1, "a", TRUE, 1 + 4i)
```

##### **Matrix**

```{r}
# Example of Matrix
m <- matrix(c(1:3))
```

##### **Factor**

```{r}
# Example of Factor
f <- factor(c(
  "Male",
  "Female",
  "Female",
  "Male",
  "Male",
  "Female"
))
```

##### **Dataframe**

```{r}
df_student <- data.frame(
  name = c("Dito", "Dian", "Rosidi"),
  age = c(22, 23, 27),
  sex = c("Male", "Female", "Male")
)
```

#### **Function**

A function is a set of command lines or code arranged together to perform a specific task. In R, we can use built-in functions or create new ones.

##### **Built-in / Base Functions**

```{r}
# Creating Age Vectors
age <- c(22, 23, 21, 8, 10, 14, 15)
```

```{r}
# Calculates the average age
mean(age)
```

##### **Custom Function**

```{r}
# Create a function to calculate Return of Investment
roi <- function(profit, cost_of_investment) {
  return((profit / cost_of_investment) * 0.1)
}
```

```{r}
# Using the ROI function that has been created
roi(profit = 175, cost_of_investment = 75)
```

#### **Package**

R Package is a collection of functions / functions or data in R. There are many packages created / developed by other users. To be able to use the existing functions in a package, we must install and load the package first. The following are examples of packages that are commonly used.

##### **Readxl: Import Excel Data**

The readxl package is useful for importing data in .xlsx or .xls format into the R environment.

```{r eval=FALSE, include= TRUE}
# Install package
install.packages("readxl")
```

```{r}
# Load package
library(readxl)
```

```{r message=FALSE, warning=FALSE}
# Import .xlsx data
df_xlsx <- read_xls("data/Superstore.xls")
```

```{r}
# View Data
df_xlsx
```

##### **Readr: Import CSV Data**

The readr package is useful for importing data in .csv format or other text formats into the R environment.

```{r eval=FALSE, include= TRUE}
# Install package
install.packages("readr")
```

```{r}
# Load package
library(readr)
```

```{r message=FALSE, warning=FALSE}
# Import .csv data
df_csv <- read_csv("data/Superstore.csv")
```

```{r}
# View Data
df_csv
```

##### **Dplyr: Data Transformation**

Dplyr is an R package that is widely used for data transformation and exploration.

```{r eval=FALSE, include= TRUE}
# Install package
install.packages("dplyr")
```

```{r}
# Load package
library(dplyr)
```

The following are some examples of common functions from the dplyr package.

###### **Select**

The first function is `select()` which is used to select a particular column.

```{r}
# Select variabel "order_date" dan "customer_name"
df_select <- select(df_csv, c("order_date", "customer_name"))

# Show the first 6 row
head(df_select)
```

###### **Filter**

The next function is the `filter()` function which functions to filter data based on a condition.

```{r}
# Filter segment = Corporate
df_filter <- filter(df_csv, segment == "Corporate")

# Show the first 6 row
head(df_filter)
```

###### **Mutate**
The `mutate()` function can be used to create new variables.

```{r}
# Create a new variable using the mutate()
df_mutate <- mutate(df_csv, cost = sales - profit)

# Show the first 6 row
head(df_mutate)
```

##### **summarise**
The `summarise()` function is used to summarize several data values ​​into a single value. This function will be very useful when combined with other functions in `dplyr`. The summarise functions that can be used include `mean()`, `median()`, `sd()`, `min()`, `max()`, `quantile()`, `first()`, `last ()`. For example, we will calculate the average sales.

```{r}
# Calculate the average sales
df_summarise <- summarise(df_csv, mean(sales))

# Show calculation results 
print(df_summarise)
```



##### **Arrange**
The `arrange()` function can be used to sort values by a column.

```{r}
# Sort data by "profit"
df_arrange <- arrange(df_csv, profit)

# Show the first 6 row
head(df_arrange)
```

##### **Pipe**
The pipe function denoted by the notation `%>%` is used to create a continuous function.

```{r}
# Finding the average sales rate for the corporate segment 
df_pipe <- df_csv %>%
  filter(segment == "Corporate") %>%
  summarise(mean(sales))

# Show calculation results 
print(df_pipe)
```

------------------------------------------------------------------------

### **Post Test**

1.  Create a dataframe containing information from 10 of your classmates (Name, Age, Gender, Hobbies)

2.  Create a function to calculate the Return on Equity

3.  Find out the 5 R packages and explain their functions/purpose
