---
title: "**Modul 2: Data Visualization**"
author: "Muhammad Apriandito - Digital Business Experience"
output:
  html_document:
    theme: paper
    highlight: tango
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "png", 
                      dev.args = list(type = "cairo-png"), 
                      fig.height = 5, 
                      fig.width = 9, 
                      tidy='styler', tidy.opts=list(strict=FALSE), 
                      fig.align = "center")
options(scipen=10000)
```

------------------------------------------------------------------------

### **Modul Description**

Data visualization is the graphical representation of information and data. By using visual elements like charts, graphs, and maps, data visualization tools provide an accessible way to see and understand trends, outliers, and patterns in data.

------------------------------------------------------------------------

### **Reading Material**

Please read the following materials.

1.  R Graphic Cockbook: <https://r-graphics.org/>

2.  Data Visualization with R: <https://rkabacoff.github.io/datavis/>

------------------------------------------------------------------------

### **Pretest**

Based on the reading materials, please answer the following questions and submit it via google classroom before the class starts.

1.  If you want to see the distribution of a discrete data, what visualization chart should you use?

2.  If you want to see a comparison of 2 continuous variables, what visualization chart should you use?

3.  Mention at least 2 R packages that are commonly used to visualize data in R?

------------------------------------------------------------------------

### **Case: Superstore Retail**

Superstore is a retail company in the United States that sells a variety of office and household equipment. The superstore has an e-commerce platform where customers can order goods online through the platform.The E-commerce platform has been operating since January 2014.

Every transaction that occurs on the platform is always recorded and stored in the Superstore database. The data stored in the form of purchase information, customer information, product information and so on. Detailed information about the data recorded can be seen in the following table.

|      Data       | Description                                          |
|:---------------:|:-----------------------------------------------------|
|   `order_id`    | Unique code to distinguish each purchase transaction |
|  `order_date`   | Order date                                           |
|   `ship_date`   | Delivery date                                        |
|   `ship_mode`   | Shipping method                                      |
|  `customer_id`  | Unique code to distinguish each customer transaction |
| `customer_name` | Customer's name                                      |
|    `segment`    | Customer segmentation                                |
|    `country`    | Customer country                                     |
|     `city`      | Customer city                                        |
|     `state`     | Customer state                                       |
|  `postal_code`  | Customer postal code                                 |
|    `region`     | Customer region                                      |
|  `product_id`   | Unique code to distinguish each product              |
|   `category`    | Product category                                     |
|  `subcategory`  | Product subcategory                                  |
| `product_name`  | Product name                                         |
|     `sales`     | Total Sales                                          |
|   `quantity`    | The quantity of goods purchased                      |
|   `discount`    | Purchase discount                                    |
|    `profit`     | Total profit for the company                         |

This data can be accessed via the following link <https://github.com/apriandito/dataset/blob/main/Superstore.xls>. Based on this data, the management wants to know how the company's performance and customer purchasing patterns.

#### **Setup**

To perform data visualization in R. We need to install and load R pakcage to be used. To install a package we can use the `install.packages("package_name")` command, and to load a package we can use the command `library("package_name")`

```{r eval=FALSE, include= TRUE}
# Install Packages
install.packages("readxl")
install.packages("ggplot2")
install.packages("dplyr")
install.packages("lubridate")
install.packages("tidyr")
install.packages("scales")
```

```{r message=FALSE, warning=FALSE}
# Activate Packages
library("readxl")
library("ggplot2")
library("dplyr")
library("lubridate")
library("tidyr")
library("scales")
```

After the required R packages are installed and loaded, we can load our data into the R environment.

```{r message=FALSE, warning=FALSE}
# Load data to R environtment
data <- read_xls("data/Superstore.xls")
```

```{r}
# Show the first 6 rows of data
head(data)
```

#### **Sales**

First of all, the management wants to know their sales trend. To display trend data continuously we can use a line chart.

```{r message=FALSE, warning=FALSE}
# Visualize sales trend
data %>%
  select(order_date, sales) %>%
  mutate(order_month = floor_date(order_date, "month")) %>%
  group_by(order_month) %>%
  mutate(monthly_sales = sum(sales)) %>%
  ungroup() %>%
  select(order_month, monthly_sales) %>%
  distinct() %>%
  ggplot(aes(x = order_month, y = monthly_sales)) +
  geom_line() +
  geom_smooth(method = "lm") +
  labs(
    title = "Sales Trend",
    subtitle = "Superstore Company",
    x = "",
    y = "Sales"
  ) +
  theme_minimal()
```

It can be seen that the number of sales increases over time. But the management has an additional question, Is this increasing number of sales followed by an increase in profit?

```{r message=FALSE, warning=FALSE}
# Visualize sales trend
data %>%
  select(order_date, profit) %>%
  mutate(order_month = floor_date(order_date, "month")) %>%
  group_by(order_month) %>%
  mutate(monthly_profit = sum(profit)) %>%
  ungroup() %>%
  select(order_month, monthly_profit) %>%
  distinct() %>%
  ggplot(aes(x = order_month, y = monthly_profit)) +
  geom_line() +
  geom_smooth(method = "lm") +
  labs(
    title = "Profit Trend",
    subtitle = "Superstore Company",
    x = "",
    y = "Profit"
  ) +
  theme_minimal()
```

#### **Customer**

The management is very satisfied to see that their sales trend continues to increase. However, to improve Customer Relationship Management, Management wants to know the purchasing patterns of its customers. In the beginning, the Management wants to know which city has the highest number of sales.

```{r}
data %>%
  select(sales, state) %>%
  group_by(state) %>%
  mutate(state_sales = sum(sales)) %>%
  ungroup() %>%
  select(state, state_sales) %>%
  distinct() %>%
  arrange(desc(state_sales)) %>%
  slice_head(n = 5) %>%
  ggplot(aes(x = reorder(state, -state_sales), y = state_sales, fill = state_sales))  +
  geom_col() +
  labs(
    title = "Top 5 cities with the highest sales",
    subtitle = "Superstore Company",
    x = "",
    y = "Sales"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

Based on the visualization above, the 5 states with the highest sales are California, New York, Texas, Washington, Pennsylvania. However, management has an additional question, are the sales of the five cities continuing to increase or is it just stagnant?

```{r message=FALSE, warning=FALSE}
data %>%
  select(order_date, sales, state) %>%
    filter(state == c(
    "California",
    "New York",
    "Texas",
    "Washington", 
    "Pennsylvania"
  )) %>%
  mutate(order_month = floor_date(order_date, "month")) %>%
  group_by(order_month, state) %>%
  mutate(monthly_sales = sum(sales)) %>%
  ungroup() %>%
  select(order_month, monthly_sales, state) %>%
  distinct() %>%
  ggplot(aes(x = order_month, y = monthly_sales, color = state)) +
  geom_line() +
  labs(
    title = "Sales Trend by State",
    subtitle = "Superstore Company",
    x = "",
    y = "Sales", 
    color = ""
  ) +
  theme_minimal() +
  theme(legend.position = "top")
```

Based on the visualization, there is no trend of increasing sales in every state. However, there are several interesting patterns that can be analyzed further, one of which is why sales in Washington increased significantly in 2017.

Furthermore, the management wants to know which segment has the highest sales for the company.

```{r}
# Mencari tahu segment pelanggan dengan pembelian terbanyak
data %>%
  select(sales, segment, profit) %>%
  group_by(segment) %>%
  mutate(sales = sum(sales)) %>%
  ungroup() %>%
  select(segment, sales) %>%
  distinct() %>%
  ggplot(aes(x = segment, y = sales, fill = sales)) +
  geom_col() +
    labs(
    title = "Total Sales in Each Customer Segment",
    subtitle = "Superstore Company",
    x = "",
    y = "", 
    fill = ""
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

Based on the visualization above, we can see that the segment that has the most sales is the "customer" segment. Sales data in each segmentation can be visualized over time to see whether there is an increasing trend or not.

```{r}
# Trend Penjualan pada masing-masing segment
data %>%
  select(order_date, sales, segment) %>%
  mutate(order_month = floor_date(order_date, "month")) %>%
  group_by(order_month, segment) %>%
  mutate(monthly_sales = sum(sales)) %>%
  ungroup() %>%
  select(order_month, monthly_sales, segment) %>%
  distinct() %>%
  ggplot(aes(x = order_month, y = monthly_sales, color = segment)) +
  geom_line() +
  labs(
    title = "Sales Trend in Each Customer Segment",
    subtitle = "Superstore Company",
    x = "",
    y = "Sales", 
    color = ""
  ) +
  theme_minimal() +
  theme(legend.position = "top")
```

The results of the visualization show that sales in each segment continue to increase every year.

#### **Product**

At the end, the management wants to know which product categories are sold the most and the product categories that generate the most profits. What product categories are most sold? Do the categories that sell a lot generate a lot of profit? we can use a bar chart to visualize it.

```{r}
# Visualize the most sold and the most profitable product categories
data %>%
  select(sales, category, profit) %>%
  group_by(category) %>%
  mutate(sales = sum(sales)) %>%
  mutate(profit = sum(profit)) %>%
  ungroup() %>%
  select(category, profit, sales) %>%
  distinct() %>%
  pivot_longer(c(sales, profit), names_to = "type", values_to = "value") %>%
  ggplot(aes(x = category, y = value, fill = type)) +
  geom_col(position = 'dodge') +
    labs(
    title = "Profit and Sales in each Product Category",
    subtitle = "Superstore Company",
    x = "",
    y = "", 
    fill = ""
  ) +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "right")
```

It turns out that the product category that sold the most is the technology category, as well as the category that generates the most profits. However, product categories that are sold more do not necessarily produce more profit. As we can see, the furniture category sells more than the office supplies category but generates less profit.

------------------------------------------------------------------------

### **Conclusion**

Data visualization can help to display information from data. This information is expected to be an insight and help companies to make better decisions.

------------------------------------------------------------------------

### **Post Test**

Answer the questions using appropriate data visualizations and interpret the results.

1.  Sales Trend of Each Product Category
2.  The city with the highest sales
3.  Sub-Category Products with highest income
